---
title: "dplyr_TP3_git"
author: "Théo Claverotte dit Laprima"
format: html
echo: false
message: false
warning: false
---


```{r}

library(here)
library(dplyr)
here::i_am("dplyr_git.Rproj")
spotify<-readRDS("top-spotify-hits-2000-2019.Rds")
```
# Exercise 1

## Question 1
```{r}
s<-spotify%>%distinct(song)
a<-spotify%>%distinct(artist)
g<-spotify%>%distinct(genre)

s2<-count(s)
a2<-count(a)
g2<-count(g)

```
the data set contains `r s2` songs of `r a2`. It contains `r s2` songs of `r g2` different musical genders.


## Question 2
```{r}
#songs_py = songs per year
songs_py <- spotify %>%
  group_by(year) %>%
  summarise(song)
spy<-count(songs_py, by=year)

library(knitr)
knitr::kable(spy)
```
This table compute the number of song per year. For example in our base at the year 2000 we can assume that we have 74 songs.

## Question 3
```{r}
artist<-spotify$artist
spotify %>% distinct(song, artist)%>%
  count(artist)%>%
  slice_max(n)

#on fait group_by puis summarise ou bien count

```

The most popular artist in the data set is Rihanna. Every song is only count once. Sha had made 23 songs. 

## Question 4
```{r}
spotify %>% 
  distinct(song, tempo, genre, keep_all=TRUE) %>%
  group_by(genre) %>%
  summarise(mean(tempo), min(tempo), max(tempo), median(tempo), n())
```




## Question 5
```{r}
data_frame<-spotify %>% 
  distinct(year, danceability, energy) %>%
  group_by(year) %>%
  summarise(nrgy=median(energy), dnce=median(danceability))
print(data_frame)
  
```

## Question 6

```{r}
library(ggplot2)
ggplot(data_frame) + geom_line(aes(x=year, y=nrgy, color="darkred")) + geom_line(aes(x=year, y=dnce, color="darkviolet")) + ylab("medians of the energy and danceability") 
```

# Exercise 2

```{r}
dropout <-readRDS("dropout.Rds")
```

## Question 1
```{r}
age_median_by_g_ms <- dropout %>%
  group_by(Gender, `Marital status`)%>%
  summarise(n(), age_med=median(`Age at enrollment`))
print(age_median_by_g_ms)
```

## Question 2
```{r}
library(tidyr)
Ages_median <- age_median_by_g_ms %>%
  group_by(Gender, `Marital status`) %>%
  pivot_wider(names_from=Gender, values_from=age_med)
print(Ages_median)
library(knitr)
knitr::kable(Ages_median)
```

## Question 3
```{r}

conditionnal_means<-dropout%>%
  group_by(Target) %>%
  summarise(across(starts_with("Curricular units"), mean))
print(conditionnal_means)
```

## Question 4

```{r}
conditionnal_means_2<- conditionnal_means %>% 
  pivot_longer(starts_with("Curricular units"), names_to = "Units") %>% 
  pivot_wider(names_from = Target)
knitr::kable(conditionnal_means_2)
```

